Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
Added a slightly more informative plan for related work and acknowledged the authors of SF for writing an awesome book.

@@

We would like to thank Jon Sailor for chatting with us on the phone to help work
through some of the more difficult problems we ran into using Coq.

>>>>

Discuss:

\begin{itemize}
  \item Proof carrying code
  \item Proof assistants
  \item Verified languages and compilers
  \item Information flow languages
\end{itemize}

@@

We would like to thank Jon Sailor for chatting with us on the phone for hours to
help work through some of the more difficult problems we ran into using Coq.
Also, we would like to thank the authors of Software
Foundations~\cite{Pierce:sf}, which was the primary resource for learning Coq
for both authors.
